Stack Safety as a Security Property

### 2020-06-26 main.tex
NOtE
Cleaned up conf

\judgment{}{\(\obsT \lesssim \obsT\)}

\judgment{}{\(\tau \lesssim \obsT\)}

\judgmenttwo{\(\obsT_1 = \tau \obsT_1'\)}{\(\obsT_1' \lesssim \obsT_2\)}
            {\(\obsT_1 \lesssim \obsT_2\)}

\judgmenttwo{\(\obsT_2 = \tau \obsT_2'\)}{\(\obsT_1 \lesssim \obsT_2'\)}
            {\(\obsT_1 \lesssim \obsT_2\)}

\judgmentthree{\(\obsT_1 = w \obsT_1'\)}
              {\(\obsT_2 = w \obsT_2'\)}
              {\(\obsT_1' \lesssim \obsT_2'\)}
              {\(\obsT_1 \lesssim \obsT_2\)}

@@

\leo{Should we point out here the edge cases of all-tau traces?}

% Fixed by Andrew:
%    \COQ{this should be equivalent to the coq version, and we should adopt it.}
%    \leo{We had this, but it was much harder to work with for my proofs. We should still
%      prove them equivalent if we want to present it this way (which is probably cleaner for
%      presentation purposes)}

Let the predicate \(\isinf(T)\) hold when the trace $T$ is infinite.
We then define {\em policy-sensitive observational equivalence}: a
trace $\MPT \in \MPOTRACE$ is equivalent to a trace $\machT \in
\MOTRACE$ if (1) \(\MPT\) is infinite and the observations of \(\MPT\)
and \(\machT\) are equivalent, or (2) if the \(\MPT\) is finite (due to a
policy fault) and its observations are a prefix of those of M.

% Fixed by Sean
%\leo{Why $\mathit{Obs}$ and not $\pi_o$ defined earlier?}
\judgmenttwo{\(\neg \isinf(\MPT)\)}{\(\pi_o(\MPT) \lesssim \pi_o(\machT)\)}
            {\(\MPT \sim_P \machT\)}

\judgmenttwo{\(\isinf(\MPT)\)}{\(\pi_o(\MPT) \simeq \pi_o(\machT)\)}
            {\(\MPT \sim_P \machT\)}

@@

Confidentiality is a noninterference-style property, comparing the
behavior of a program with an arbitrary variant that preserves low
confidentiality data but may have any configuration of high
confidentiality data.

\definition{Variations}

We say two machine states $\mach$ and $\mach'$ are {\em variations} of one
another given a contour $\contour$ if they agree on low
confidentiality data:
  \[\mach \approx_\contour \mach' \triangleq \forall \component .
    \contour(\component) = \LOWSEC \rightarrow \mach(\component) =
    \mach'(\component)\]

@@

A system satisfies eager {\em stack confidentiality} with respect to a
call map \(\callmap\) and a code map \(\codemap\) if for any initial
mpstate $\mpstate{\mach_0}{\pol_0}$
%\(\mpstatename = \mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\)
and each adjacent pair of a call state \(\mach_c\) and state
\(\mach_e\) with policy state \(\pol_e\) in the induced trace from
\(\mpstatename\), where \(\callmap(\mach_c(\PCname)) = n\) and
\(\codemap(\mach_e(\PCname)) = \funid\), one of two cases holds on the
induced traces from \(\mpstate{\mach_e}{\pol_e}\) and any variation
\(\mach_e'\) with respect to the contour
\(\mathit{Cof}(\mach_c,\funid,n)\):

\begin{itemize}
\item
If the trace from the call reaches a return -- \(\mpstate{\mach_e}{\pol_e}
  \hookrightarrow_P \MPT | \ret{\mach_c}\) -- then the trace from the variant
  \(\mach_e'\) reaches a return -- \(\mach_e' \hookrightarrow \machT |
  \ret{\mach_c}\). Let \(\mach_r\) and \(\mach_r'\) be the final states of
  \(\pi_m(\MPT)\) and \(\machT\), respectively. Until their final states,
  \(\MPT\) and \(\machT\) must be observationally equivalent, \(\pi_o(\MPT)
  \cdot \tau \eqsim \pi_o(\machT) \cdot \tau\). For any component
  \(\component\) where \(\mach_e(\component) \not = \mach_r(\component)\) or
  \(\mach_e'(\component) \not = \mach_r'(\component)\),
  \(\mach_r\) agrees with \(\mach_r'\) on \(\component\).
\item
  If the trace from the call never reaches a return, neither does the
  trace from the variant. Then if \(\mpstate{\mach_c}{\pol_c} \hookrightarrow_P
  \MPT\) and \(\mach_c' \hookrightarrow \machT\), \(\MPT \sim_P \machT\).
\end{itemize}

  \leo{Think more about whether we vary mc or step mc}
  \sna{I've left it at step mc for now}

>>>>

\leo{TODO: We really need a better layout than centered paragraphs.}
\judgment{}{\(\obsT \lesssim \obsT\)}

\judgment{}{\(\tau \lesssim \obsT\)}
\judgment{}{\(w \lesssim w\obsT\)}

\judgment{\(\obsT_1 \lesssim \obsT_2\)}
         {\(\tau \obsT_1 \lesssim \obsT_2\)}

\judgment{\(\obsT_1 \lesssim \obsT_2\)}
         {\(\obsT_1 \lesssim \tau \obsT_2\)}

\judgment{\(\obsT_1 \lesssim \obsT_2\)}
         {\(w\obsT_1 \lesssim w\obsT_2\)}

@@

\leo{Rephrase transition. I hate it:} There are two interesting things
to note.  First, observation trace equivalence could alternatively be
defined as the prefix relation but dropping the only assymetric rules
\leo{2 + 3. TODO: name rules?}

\leo{Also rephrase this.}
Second, an infinite silent trace is a prefix of (and equivalent to)
any other trace. While this might seem surprising at first, it makes
sense in a timing-insensitive context: an external observer looking
at two machine runs cannot distinguish between a machine that
steps forever or a machine that steps for a long time before producing
some output, before that time has passed.

%Let the predicate \(\isinf(T)\) hold when the trace $T$ is infinite.
%We then define {\em policy-sensitive observational equivalence}: a
%trace $\MPT \in \MPOTRACE$ is equivalent to a trace $\machT \in
%\MOTRACE$ if (1) \(\MPT\) is infinite and the observations of \(\MPT\)
%and \(\machT\) are equivalent, or (2) if the \(\MPT\) is finite (due to a
%policy fault) and its observations are a prefix of those of M.
% 
%% Fixed by Sean
%%\leo{Why $\mathit{Obs}$ and not $\pi_o$ defined earlier?}
%\judgmenttwo{\(\neg \isinf(\MPT)\)}{\(\pi_o(\MPT) \lesssim \pi_o(\machT)\)}
%            {\(\MPT \sim_P \machT\)}
% 
%\judgmenttwo{\(\isinf(\MPT)\)}{\(\pi_o(\MPT) \simeq \pi_o(\machT)\)}
%            {\(\MPT \sim_P \machT\)}

@@

Confidentiality is a noninterference-style property, comparing the
behavior of a machine with an arbitrary variant that preserves low
confidentiality data.

\leo{Variations or variants?}
\definition{Variations}

We say two machine states $\mach$ and $\mach'$ are {\em variations} of one
another given a contour $\contour$ if they agree on low
confidentiality data:
%
\[
\mach \approx_\contour \mach' \triangleq \forall \component .
\contour(\component) = \LOWSEC \rightarrow \mach(\component) =
\mach'(\component)
\]

Let $\callmap$ be a call map and $\codemap$ a code map.
Confidentiality with respect to $\callmap$ and $\codemap$ should be
enforced at {\em every} transition between a caller $f$ and a callee
$f'$.
%
Suppose that an execution trace starting from some initial
machine-policy state pair contains such a transition. That is, it
contains some step between state state pairs $(\mach_c,\pol_c)
\stepstoobs{\obs}_P (\mach_e, \pol_e)$ for some observation $\obs$
such that $\mach_c$ is a valid call with $n$ arguments
($\callmap(\mach_c(\PCname)) = n$) and $\mach_e$ is an entry point for
$f'$ ($\codemap(\mach_e(\PCname)) = f'$).

Now let $MP$ be the (potentially infinite) prefix of the trace
starting at the entry $(\mach_e, \pol_e)$ until the corresponding
return: $(\mach_e, \pol_e) \hookrightarrow MP ~ | ~ \ret{\mach_c}$ and
$\contour$ be the contour at the call: $\contour =
\mathit{Cof}(\mach_c, f', n)$.

\definition{Trace Confidentiality}

We will say that $MP$ satisfies {\em trace confidentiality} with
respect to $\callmap$, $\codemap$, and $\contour$ if, for every
$\contour$-variation $\mach_e'$ of the entry state, and the prefix $M$
of its induced traced until the corresponding return $\mach_e'
\hookrightarrow M ~ | ~ \ret{\mach_c}$, one of three cases holds:
\begin{itemize}
\item If the call successfully returns, that is $MP$ is finite and its
  final state $\mach_r$ is a valid return, then $M$ must also be
  finite with some final state $\mach_r'$ that has changed in the same
  manner:
$$\forall \component. ~ \mach_e(\component) \not = \mach_r(\component)
  \vee \mach_e'(\component) \not = \mach_r'(\component) \rightarrow
  \mach_r(\component) = \mach_r'(\component)$$

  In addittion their observations must be equivalent:
  $$\pi_o(MP) \eqsim \pi_o(M)$$
\item If the call trace never returns and is infinite, then the
  variant trace must also never return and their observations are
  equivalent:
  $$\pi_o(MP) \eqsim \pi_o(M)$$  
\item Finally, if the call trace ends prematurely with a policy fault,
  then we require that the observations of $MP$ are a prefix of those
  of the variation:
  $$\pi_o(MP) \lesssim \pi_o(M)$$
\end{itemize}

@@

We say that a system satisfies {\em stack confidentiality} with
respect to a call map $\callmap$ and a code map $\codemap$ if for
every initial machine-policy pair $(\mach_0, \pol_0)$ and its induced
trace, every call subtrace\leo{Can i reuse stuff above?} in it
satisfies trace confidentiality.
